ManuscriptPURFits

### 2024-01-29 Code/ManuscriptPURFits.Rmd
Simplify code , removed redundant variables

Make O2_uM and WL as factor levels from highest to lowest
```{r O2 levels}

PURPARFits <- PURPARFits %>%
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL= factor(WL, levels = c("WW", 660, 530, 450)),
        Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )))

@@

#DummyDF for SS120; SS120 is a low light strain, based on literature it can only grow up to 300 uE WW; SS120 consistently died at various light colors and oxygen levels latest at ~PUR 400; it can safely be assumed it dies at par_ue = 0
Dummy_Strain <- c("SS120")
Dummy_Photoperiod <- c(4, 8, 12, 16)
Dummy_Par_ue<- c(0)
Dummy_O2_uM <- c(2.5, 25.0, 250.0)
Dummy_WL <- c(450, 530, 660, "WW")
Dummy_deltaOD_Lmu_corr <- c(0)
Dummy_Pur_ue<- c(0)
Dummy_deltaOD_Lmu_corr_day <- c(0)
Dummy_PUR_day <- c(0)

@@

# PURPARFits_dummy <- PURPARFits_dummy %>% 
#   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          WL= factor(WL, levels = c("WW", 660, 530, 450)),
#         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )))

@@

```{r testplot}
 PURPARFits %>% 
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
    scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
  facet_grid(rows = vars(Par_ue), cols = vars(Strain)) +
  theme_bw()
```

@@

# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero. As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
PURPARStrainO2NestDummy_filtered <- PURPARFits_dummy |>
  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
                            TRUE ~ 0)) |>
   filter(remove == 0,
          PURPhotonDose_day <= 1.5e+06) |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

PURPARStrainO2NestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR, 0 growth rates
#Note: fit fails for SS120, 12h photoperiod and O2 = 25uM. Works if I remove outlier(WL = 660 and PAR = 30 or MiSa1456) 
PURPARStrainO2PhotoperiodNestDummy <- PURPARFits_dummy |>
   filter(SampleID != "MiSa1456") %>% 
   # filter(SampleID != "JuNa1068") %>% 
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2WLNestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "WL")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2PeriodWLNestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

@@

```{r growthPURplots, fig.height= 10, fig.width= 10}
#ReplicateMean_

@@

# PURPARStrainO2NestDummy |>
#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#     labs(title = "PURPARStrainO2NestDummy GRC") +
#   theme_bw()

@@

PURPARStrainO2NestDummy |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestDummy Platt") +
  theme_bw()

PURPARStrainO2NestDummy_filtered|>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestDummy_filtered Platt") +
  theme_bw()

# PURPARStrainO2PhotoperiodNest |>
#   filter(!map_lgl(GRC_Model, is.null)) |>
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoperiodNest GRC") +
#   theme_bw()

# PURPARStrainO2PhotoperiodNestDummy |>
#    filter(!map_lgl(GRC_Model, is.null)) |>
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoperiodNestDummy GRC") +
#   theme_bw()

# PURPARStrainO2PhotoperiodNest |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoperiodNest Platt") +
#   theme_bw()

PURPARStrainO2PhotoperiodNestDummy |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +   
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoperiodNestDummy Platt") +
  theme_bw()

PURPARStrainO2PhotoperiodNestDummy |>
  filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(GRClm_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
   scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoperiodNestDummy Linear Model") +
  theme_bw()

PURPARStrainO2PhotoperiodNestDummy |>
  unnest(data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  # geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
     scale_colour_manual(values = MCMIXColours) +
    facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoperiodNestDummy all data no fits") +
  theme_bw()

>>>>

Make O2_uM and WL as factor levels from highest to lowest and remove all green light (WL= 530) growth data
```{r O2 levels}

PURPARFits <- PURPARFits %>%
  filter(WL %in% c("WW", 660, 450)) %>% 
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL= factor(WL, levels = c("WW", 660, 450)),
        Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )))

@@

#DummyDF for SS120; SS120 is a low light strain, based on literature it can only grow up to 300 uE WW; SS120 consistently died at various light colors and oxygen levels latest at ~PUR 400; it can safely be assumed it dies at par_ue = 0
Dummy_Strain <- c("SS120")
Dummy_Photoperiod <- c(4, 8, 12, 16)
Dummy_Par_ue<- c(0)
Dummy_O2_uM <- c(2.5, 25.0, 250.0)
Dummy_WL <- c(450, 660, "WW")
Dummy_deltaOD_Lmu_corr <- c(0)
Dummy_Pur_ue<- c(0)
Dummy_deltaOD_Lmu_corr_day <- c(0)
Dummy_PUR_day <- c(0)

@@

remove(DummyDF_Expand)

@@

```{r testplot}
 PURPARFits %>% 
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
    scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
  facet_grid(rows = vars(Par_ue), cols = vars(Strain)) +
  theme_bw()
```

@@

# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero. As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
PURPARStrainO2NestModels_filtered <- PURPARFits_dummy |>
  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
                            TRUE ~ 0)) |>
   filter(remove == 0,
          PURPhotonDose_day <= 1.5e+06) |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# PURPARStrainO2NestModels <- PURPARFits_dummy |>
#   nest(data = -c("Strain","O2_uM")) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100),
#                               control = list(maxiter = 500)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          ) |>
#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
#                               data = .x,
#                               start = LinEqnStart
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRClm_Param = map(GRClm_Model, tidy),
#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
#          GRClm_Glance = map(GRClm_Model, possibly(glance))
#          )

# # model with dummy dark, 0 PAR, 0 growth rates
# PURPARStrainO2PhotoNestModels <- PURPARFits_dummy  |>
#  nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-8, b = 1e-9, Pmax = 1),
#                               lower = c(-0, 0, 0),
#                               upper = c(1,1,100),
#                               control = list(maxiter = 500)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          ) |>
#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
#                               data = .x,
#                               start = LinEqnStart
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRClm_Param = map(GRClm_Model, tidy),
#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
#          GRClm_Glance = map(GRClm_Model, possibly(glance))
#          )

PURPARStrainO2PhotoNestModels_filtered <- PURPARFits_dummy |>
   filter(PURPhotonDose_day <= 1.5e+06) |>
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# # model with dummy dark, 0 PAR,  growth rates 
# PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
#   nest(data = -c("Strain","O2_uM", "WL")) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100),
#                               control = list(maxiter = 500)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )|>
#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
#                               data = .x,
#                               start = LinEqnStart
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRClm_Param = map(GRClm_Model, tidy),
#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
#          GRClm_Glance = map(GRClm_Model, possibly(glance))
#          )
# 
# 
# # model with dummy dark, 0 PAR,  growth rates
# PURPARStrainO2PeriodWLNest <- PURPARFits_dummy |>
#   nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100),
#                               control = list(maxiter = 500)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )|>
#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
#                               data = .x,
#                               start = LinEqnStart
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRClm_Param = map(GRClm_Model, tidy),
#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
#          GRClm_Glance = map(GRClm_Model, possibly(glance))
#          )

@@

# Plot fits
```{r growthPURplots, fig.height= 10, fig.width= 10}
#ReplicateMean_

@@

# PURPARStrainO2NestModels |>
#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#     labs(title = "PURPARStrainO2NestModels GRC") +
#   theme_bw()

@@

# PURPARStrainO2NestModels |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |> # only include fits that did not fail
#   unnest(GRCplatt_Predict, data) |>
#    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
#          Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#   labs(title = "PURPARStrainO2NestModels Platt") +
#   theme_bw()

PURPARStrainO2NestModels_filtered|>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestModels_filtered Platt") +
  theme_bw()

# PURPARStrainO2PhotoNestModels |>
#   filter(!map_lgl(GRC_Model, is.null)) |>
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoNestModels GRC") +
#   theme_bw()

# PURPARStrainO2PhotoNestModels |>
#    filter(!map_lgl(GRC_Model, is.null)) |>
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoNestModels GRC") +
#   theme_bw()

# PURPARStrainO2PhotoNestModels |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoNestModels Platt") +
#   theme_bw()

PURPARStrainO2PhotoNestModels_filtered |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +   
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoNestModels_filtered Platt") +
  theme_bw()

PURPARStrainO2PhotoNestModels_filtered |>
  filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(GRClm_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
   scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoNestModels_filtered Linear Model") +
  theme_bw()

PURPARFits_dummy |>
  # unnest(data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  # geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
     scale_colour_manual(values = MCMIXColours) +
    facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoNestModels all data no filter") +
  theme_bw()

# PURPARStrainO2WLNestModels |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
#          Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2WLNestModels Platt") +
#   theme_bw()
